---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ggrama

<!-- badges: start -->
[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
[![License: MIT](https://img.shields.io/badge/License-MIT-blue.svg)](https://opensource.org/licenses/MIT)
[![DOI](https://zenodo.org/badge/424568391.svg)](https://zenodo.org/badge/latestdoi/424568391)
<!-- badges: end -->

The goal of ggrama is to make it easy to plot Ramachandran diagrams from a pdb file using ggplot2 graphics.

## Installation

You can install the development version of ggrama:

``` r
devtools::install_github("missuse/ggrama")
```

## Example  

```{r example, fig.width = 4,  fig.height = 4, out.width = "50%", fig.align = 'center'}
library(ggrama)

#download a pdb file
download.file("https://files.rcsb.org/download/2ADQ.pdb1.gz",
              dest = "2ADQ.pdb1.gz")

#plot by type of Ramachandran diagrams
ggrama("2ADQ.pdb1.gz") #general type the default
ggrama("2ADQ.pdb1.gz", "pre.pro") #pre-proline, additional options are glycine and proline
```

Or plot all four types in a grid

```{r example2, fig.width = 8,  fig.height = 8}
ggrama_all("2ADQ.pdb1.gz")

```

Using contours:

```{r example3, fig.width = 8,  fig.height = 8}
ggrama_all("2ADQ.pdb1.gz",
           contour = TRUE) #contours
```


```{r example4, fig.width = 8,  fig.height = 8}
ggrama_all("2ADQ.pdb1.gz",
           contour = TRUE, #contours
           smooth = TRUE) #use smoothed background
```

## Citation

To cite `ggrama` in publications use:

> Milan Dragićević (2021), ggrama: Ramachandran diagrams using ggplot2 graphics. url: https://github.com/missuse/ggrama. doi: 10.5281/zenodo.5660975

A BibTeX entry for LaTeX users is

```{}
  @Manual{,
    title = {ggrama: Ramachandran diagrams using ggplot2 graphics},
    author = {Milan Dragićević},
    year = {2021},
    url = {https://github.com/missuse/ggrama},
    doi = {https://doi.org/10.5281/zenodo.5660975},
  }
```
